Heatmaps of pleiotropy test statistics - all nonlocals and all locals with LOD above 15

### 2019-07-16 analysis/paper/heatmaps-pleiotropy-statistics-subset-locals.Rmd
added Rmd files for heatmaps

---
title: "Heatmaps of pleiotropy test statistics - all traits above LOD 10"
author: "Frederick Boehm"
date: "7/15/2019"
output: 
  html_document:
    toc: true
    code_folding: hide
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(hotspots)
pleio_threshold <- 4
ult <- 10 # univariate lod threshold
```

Below, we produce heatmaps for every hotspot. We consider, for every hotspot, all local and nonlocal traits with univariate LOD at least `r ult`. Note that the choice of `r ult` is arbitrary and limits the sets of traits to those that are rather strongly associated.

In future analyses, we might subset only the local traits... ie, use only the strongest local traits and all of the nonlocals

@@

```{r make_nonlocal_annot-2}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= ult) %>% #genomewide threshold
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_nonlocal_annot-5}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= ult) %>% #genomewide threshold
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_nonlocal_annot-7}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= ult) %>% #genomewide threshold
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_nonlocal_annot-11}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= ult) %>% #genomewide threshold
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_nonlocal_annot-13}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= ult) %>% #genomewide threshold
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

>>>>

---
title: "Heatmaps of pleiotropy test statistics - all nonlocals and all locals with LOD above 15"
author: "Frederick Boehm"
date: "7/16/2019"
output: 
  html_document:
    toc: true
    code_folding: hide
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(hotspots)
pleio_threshold <- 4
ult <- 15 # univariate lod threshold
```

Below, we produce heatmaps for every hotspot. We consider, for every hotspot, all local traits with univariate LOD at least `r ult` and all nonlocal traits. Note that the choice of `r ult` is arbitrary and limits the sets of traits to those that are rather strongly associated.

@@

```{r make_nonlocal_annot-2}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_nonlocal_annot-5}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
#  filter(lod >= ult) %>% #genomewide threshold
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_nonlocal_annot-7}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
#  filter(lod >= ult) %>% #genomewide threshold
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_nonlocal_annot-11}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
#  filter(lod >= ult) %>% #genomewide threshold
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_nonlocal_annot-13}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
#  filter(lod >= ult) %>% #genomewide threshold
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```
